Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-07-14 mu/article/article.tex
Minimal correction.
Adding new plots to better explain the results.

\documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external
                        % documents and URLs 
\usepackage{blindtext}  % fill text
\usepackage[dvipsnames]{xcolor}
\usepackage{multirow}
\usepackage[capitalize]{cleveref}
% \usepackage{showframe}
\usepackage[inline]{showlabels}

@@

Using those structures we address a theoretical study of the spin velocity
injection (SVI) by one-photon absorption of linearly polarized light.
% 
% We calculated the responses for the particular cases when the spin of
% electrons is directed along the the $z$ Cartesian coordinate, perpendicular
% to the $xy$ plane of the structure, or for the case when the velocity is
% directed along the $x$ and $y$ Cartesian direction on the $xy$ plane of the
% structures.
{\color{red}
% 
Because we have 2D structures we made the analysis for tow cases. The first is
fixing the spin of the electrons along the $z$ Cartesian direction with the
velocity directed on the surface of the structure in the $xy$ plane. The second
is fixing the spin velocity in the $x$ or $y$ direction and the spin directed
in $xyz$.}
% 
The SVI is an optical effect that quantifies the velocity at which a PSC moves
along the Cartesian direction $\mathrm{a}$ with the spin of electron polarized
along the Cartesian direction $\mathrm{b}$. One photon absorption of linearly
polarized light can promote a distribution of electrons in $\mathbf{k}$ space
regardless the symmetry of the material resulting in a null electrical current.
Then, the electrons excited to the conduction bands at opposite $\mathbf{k}$
points will result in opposite spin polarizations producing no net spin
injection.\cite{bhatPRL05} If the crystalline structure of the material is
noncentrosymmetric the spin polarization injected at a given $\mathbf{k}$ point
could not vanish\cite{alvaradoPRL85, schmiedeskampPRL88} 
% 
{\color{red}
% 
and then, since the velocities of electrons at opposite $\mathbf{k}$ points are
opposite, a pure spin current will be produced. Since the structures presented
here are noncentrosymmetric, they are good candidates in which this effect can
be induced.}

@@

\subsection{Spin velocity injection} % (fold)
\label{sec:res-spin_velocity}

\begin{table}[b]
\begin{tabular}{cccccc}
\hline
\multirow{2}{*}{Structure \quad} & 
Kind of \quad & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$}\\
\cline{5-6}
& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
\emph{up}    & 2D   & 40    & 0.09  & $\mathrm{yz}$ &  87.2    \\
             &      &       & 1.94  & $\mathrm{yz}$ &  22.2    \\
             &      &       & 1.97  & $\mathrm{yz}$ & -29.7    \\
\emph{alt}   & 2D   & 145   & 0.72  & $\mathrm{yz}$ & -40.2    \\
             &      &       & 0.91  & $\mathrm{yz}$ & -32.9    \\
 CdSe        & bulk & 90    & 0.91  & $\mathrm{zz}$ & -26.9    \\
 GaAs        & bulk & 90    & 2.31  & $\mathrm{xx}$ & -21.6    \\
\hline
\end{tabular}

@@

Using the Eq. \eqref{eq:vab-aw}, we calculated the
$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ response for the \emph{up} and
\emph{alt} 2D structures and for the CdSe and GaAs bulk systems; the results
are presented in Fig. \ref{fig:vab-str-comp}. The angle $\alpha$ presented in
the response of each structure is that for which the response is maximized in
each case.
% 
The most intense response corresponds to the \emph{up} structure centered at
0.088\,eV corresponding to the Mid Infrared (MIR) radiation and reaching a spin
velocity of 87.2\,Km/s.
% 
For an energy range from 0.66\,eV to 3.0\,eV, corresponding
to energies of the Near Infrared (NIR) to visible radiation, all
the four structures have contributions of the same order of magnitude.
% 
For this energy range the \emph{up} structure has two peaks centered at
1.94\,eV and 1.97\,eV reaching spin velocities of 22.2\,Km/s and -29.7\,Km/s and the \emph{alt} structure has two peaks centered at 0.72\,eV
and 0.91\,eV reaching spin velocities of -40.2\,Km/s and -32.9\,Km/s,
respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure response reaches the maximum for an incoming beam of energy of
2.31\,eV and resulting in a spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for
the 2D and bulk structures; a positive (negative) spin-velocity means that the
velocity moves (anti-)parallel to the electric field.
% 
From the table also we obtain that particularly the 2D \emph{up} structure is
the one with the highest response being between 4 and 5 times more intense than
the corresponding to the bulk structures.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}

    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response
    as a function of the photon energy and polarization angle $\alpha$ for the
    \emph{up} structure for two energy ranges. The absolute maxima is located
    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared
    radiation range, and two local maxima from 1.90\,eV to 1.93\,eV and from
    1.96\,eV to 2.0\,eV, in the visible radiation range, all for polarization
    angles between $25^{\circ}$ and $50^{\circ}$.}
    \label{fig:up-3d-vsz}   
\end{figure}

@@

    \caption{Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ (top frames, right
    scale of figs (a) and (b)), the corresponding velocity angle
    $\gamma_{\mathrm{z}}(\omega,\alpha)$ (top frames, right scale), the
    collinear (circled box) and perpendicular (square box) angles, and the two
    components $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
    $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ (bottom frames) for the
    \emph{up} structure fixing the energy to 0.088\,eV. }
    \label{fig:up-vaz-rag}
\end{figure}

@@

Using Eq. \eqref{eq:vs-mag}, we calculated $|\mathcal{V}_{\sigma^{\mathrm{b}}}
(\omega,\alpha)|$ and made the analysis for the case when the spin is fixed
along $z$ directed perpendicularly to the surface of the \emph{up} and
\emph{alt} structures. Also, using Eq. \eqref{eq:gamma-ang}, we determined the
angle $\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed
on the surface of the each structure.
%

\subsubsection{Up structure}

We present in Fig. \ref{fig:up-3d-vsz} the result of evaluate
$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|$ (Eq. \eqref{eq:vs-mag})
for two energy ranges on the \emph{up} structure.
% 
We obtained that the zone where the maximum response is reached corresponds to
a energy range of the incident beam from 0.084\,eV to 0.093\,eV, in the far
infrared (FIR) and polarization angles $\alpha$ between $30^{\circ}$ and
$45^{\circ}$. Also the two local maxima are held for same beam polarization
angles but for an energy range between 1.90\,eV and 2.05\,eV, in the visible
radiation range.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top panel of Fig. \ref{fig:up-vaz-rag} we present the result of evaluate
Eq. \eqref{eq:vs-mag} (left scale, black solid line) fixing the energy of the
incoming beam to 0.088\,eV for which the response is maximized as shown in the
top panel of Fig. \ref{fig:up-3d-vsz}. The absolute maximum is obtained when
the polarization angle is $\alpha = 40^{\circ}$ resulting in a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 95.8$\,Km/s. This value
comes from the contribution of the components
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)=39.8$\,Km/s and
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)=87.2$\,Km/s not presented here.
% 
In the same panel we present the corresponding velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red dashed line), that for
the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) = 65^{\circ}$. Also
we present two boxes indicating the values for which the angles of the spin
velocity and the polarization angle are parallel (Eq. \ref{eq:gamma-par}, green
circled box), corresponding to $\alpha =
\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$; and perpendicular
(Eq. \ref{eq:gamma-perp}, blue squared box), corresponding to $\alpha=155.5^
{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=65.5^{\circ}$. The green
and blue dashed arrows are directed from those angles to the respective value
of the response corresponding to
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 82.3$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 24.8$\,Km/s.
% 
We also found that the velocity angle is almost constant for all the
polarization angle range having values of $\gamma_{\mathrm{z}}(\omega,\alpha) =
65.5^{\circ}\pm 0.5^{\circ}$.
% 
In the bottom panel of Fig. \ref{fig:up-vaz-rag} we present for the same
structure the result of evaluate Eq. \eqref{eq:vs-mag} fixing now the energy of
the incoming beam to 1.972\,eV for which the response has a local maximum as
shown in the bottom panel of Fig. \ref{fig:up-3d-vsz}. The local maximum is
obtained again when the polarization angle is $\alpha = 40^{\circ}$ resulting
in a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| =
30.3$\,Km/s directed in a velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha) =
78^{\circ}$.
% 
Again, the  green circled box indicates the parallel angles $\alpha =
\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 78.5^{\circ}$ corresponding to a
spin-velocity $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
23.5$\,Km/s indicated with the green arrow
% 
and the blue squared box indicates the perpendicular pair of angles $\alpha =
155.5^ {\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha) = 65.5^{\circ}$.
% 
We found again that the velocity angle is almost constant at $78^{\circ}$ and
has variations of $\pm 1^{\circ}$ for polarization angles $0^{\circ} \leq
\alpha \leq 100^{\circ}$.
% 
We also made the analysis for the cases when the spin polarization is directed
along $\mathrm{x}$ and $\mathrm{y}$ but we do not present here the
corresponding plots. For those cases we have that the responses maxima are
obtained for an energy of 0.088\,eV and polarization angle $\alpha=40^{\circ}$
resulting in values of
$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=37.4$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=24.8$\,Km/s.

@@

\subsubsection{Alt structure}

We present in Fig. \ref{fig:alt-3d-vsb} the result of evaluate
$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|$ (Eq. \eqref{eq:vs-mag})
on the \emph{alt} structure.
% 
We obtained that the zone where the maximum response is reached corresponds to
energies from 0.90\,eV to 0.93\,eV and a local maximum is obtained
for energies between 0.67\,eV and 0.75\,eV both located in the FIR radiation
range and for polarization angles between $120^{\circ}$ and $150^{\circ}$.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top panel of Fig. \ref{fig:up-vaz-rag} we present the result of evaluate
Eq. \eqref{eq:vs-mag} (left scale, black solid line) fixing the energy to
0.912\,eV for which the response is maximized as shown in the
top panel of Fig. \ref{fig:up-3d-vsz}. The absolute maximum is obtained when
the polarization angle is $\alpha = 40^{\circ}$ resulting in a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 43.0$\,Km/s.
% 
In the same panel we present the velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red dashed line), that for
the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) = 145^{\circ}$.
% 
As explained for the previous case, the green circled box indicates the
parallel pair of angles $\alpha = \gamma_{\mathrm{z}\parallel}(\omega,\alpha) =
53.5^{\circ}$ with a corresponding value
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s indicated
with the green arrow, and the blue square box indicates the perpendicular pair
of angles, $\alpha=140^{\circ}$ and
$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$, with a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|=43.0$\,Km/s indicated with
the blue arrow.
% 
We also have that the velocity angle is centered at $51.5^{\circ}$ having
variations of $\pm 2^{\circ}$ for the polarization angle range $0^{\circ} \leq
\alpha \leq 180^{\circ}$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented
here. The absolute maxima for the cases when the spin polarization are directed
in the $x$ and $y$ direction are obtained for an energy of 0.912\,eV and
polarization angle $\alpha=145^{\circ}$ resulting in values of
$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)| = 27.1$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)| = 33.2$\,Km/s.

@@

Now, using the Eq. \eqref{eq:vv-mag}, we calculated the
$|\mathcal{V}^{\mathrm{a}} (\omega,\alpha)|$ for the case when the velocity is
fixed in the $x$ and $y$ direction on the surface of the \emph{up} and
\emph{alt} structures. Also, using the Eqns. \eqref{eq:polar-ang} and 
\eqref{eq:azimuthal-ang}, we determined the polar $\theta_{\mathrm{a}}
(\omega,\alpha)$ and azimuthal $\varphi_{\mathrm{a}} (\omega,\alpha)$ angles
corresponding to the direction of the spin.

\subsubsection{Up structure}

@@

In top and bottom panels of Fig. \ref{fig:up-3d-vva-2} we present the
result of evaluate Eq. \eqref{eq:vv-mag} for the same structure fixing the
velocity in the $x$ and $y$ direction for other range of energies that present
a intense response.
% 
From this figure we can see that the two local maxima are obtained for energies
between 1.80\,eV and 2.10\,eV, in the range of visible radiation, and
polarization angles between $30^ {\circ}$ and $45^{\circ}$.
% 
From the top and bottom panels of Fig. \ref{fig:up-vab-comp-rtp-2} we have that
$|\mathcal{V}^{\mathrm{x}} (\omega,\alpha)| =  9.8$\,Km/s and
$|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)| = 49.3$\,Km/s fixing the
polarization angle to $\alpha=40^{\circ}$ and the beam energy to 1.932\,eV.
% 
In same panels we present the corresponding polar and azimuthal spin
polarization angles that have values of $\theta_{\mathrm{x}}(\omega,\alpha) =
129^{\circ}$, $\varphi_{\mathrm{x}}(\omega,\alpha) = 229^{\circ}$,
$\theta_{\mathrm{y}} (\omega,\alpha) = 127^{\circ}$ and $\varphi_{\mathrm{y}}
(\omega,\alpha) = 227^{\circ}$ being constant all of them in the peak of the
local maxima. Then, the spin is directed downward the third Cartesian quadrant
of the $xy$ plane when it moves along $x$ and $y$ directions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Alt structure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-vxb}
    \\
    \includegraphics[width=\linewidth]{altplots/alt-3d-vyb}

>>>>

\documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}
\usepackage{amsmath}    % need for subequations 
\usepackage{graphicx}   % need for figures 
\usepackage{verbatim}   % useful for program listings 
\usepackage{color}      % use if color is used in text 
\usepackage{subfigure}  % use for side-by-side figures 
\usepackage{hyperref}   % use for hypertext links, including those to external 
                        % documents and URLs 
%\usepackage{blindtext}  % fill text 
\usepackage[dvipsnames]{xcolor}
\usepackage{multirow}
%\usepackage[capitalize]{cleveref}
% \usepackage{showframe}
\usepackage[inline]{showlabels}
\input{/Users/reinaldo/Documents/tex_files/bmsdefinitions.tex}
% \input{/Users/bms/util/definitions}

@@

Using those structures we address a theoretical study of the spin velocity
injection (SVI) by one-photon absorption of linearly polarized light.
% 
% We calculated the responses for the particular cases when the spin of
% electrons is directed along the the $z$ Cartesian coordinate, perpendicular
% to the $xy$ plane of the structure, or for the case when the velocity is
% directed along the $x$ and $y$ Cartesian direction on the $xy$ plane of the
% structures.
{
% \color{red}
% 
Because we have 2D structures we made the analysis for tow cases. The first is
fixing the spin of the electrons along the $z$ Cartesian direction with the
velocity directed on the surface of the structure in the $xy$ plane. The second
is fixing the spin velocity in the $x$ or $y$ direction and the spin directed
in $xyz$.}
% 
The SVI is an optical effect that quantifies the velocity at which a PSC moves
along the Cartesian direction $\mathrm{a}$ with the spin of electron polarized
along the Cartesian direction $\mathrm{b}$. One photon absorption of linearly
polarized light can promote a distribution of electrons in $\mathbf{k}$ space
regardless the symmetry of the material resulting in a null electrical current.
Then, the electrons excited to the conduction bands at opposite $\mathbf{k}$
points will result in opposite spin polarizations producing no net spin
injection.\cite{bhatPRL05} If the crystalline structure of the material is
noncentrosymmetric the spin polarization injected at a given $\mathbf{k}$ point
could not vanish\cite{alvaradoPRL85, schmiedeskampPRL88} 
% 
{
% \color{red}
% 
and then, since the velocities of electrons at opposite $\mathbf{k}$ points are
opposite, a pure spin current will be produced. Since the structures presented
here are noncentrosymmetric, they are good candidates in which this effect can
be induced.}

@@

\subsection{SVI: Spin velocity injection} % (fold)
\label{sec:res-spin_velocity}

\begin{table}[b]
\begin{tabular}{cccccc}
\hline
\multirow{2}{*}{Structure \quad} & 
Kind of \quad & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$}\\
\cline{5-6}
& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
\emph{up}    & 2D   & 40    & 0.088  & $\mathrm{yz}$ &  87.2    \\
             &      &       & 1.938  & $\mathrm{yz}$ &  22.2    \\
             &      &       & 1.972  & $\mathrm{yz}$ & -29.7    \\
\emph{alt}   & 2D   & 145   & 0.720  & $\mathrm{yz}$ & -40.2    \\
             &      &       & 0.912  & $\mathrm{yz}$ & -32.9    \\
 CdSe        & bulk & 90    & 0.906  & $\mathrm{zz}$ & -26.9    \\
 GaAs        & bulk & 90    & 2.312  & $\mathrm{xx}$ & -21.6    \\
\hline
\end{tabular}

@@

Using  Eq. \eqref{eq:vab-aw}, we calculated 
$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the \emph{up} and
\emph{alt} 2D structures and for CdSe and GaAs which are bulk systems; 
the results
are presented in Fig. \ref{fig:vab-str-comp}. 
The angle $\alpha$ presented in
the response of each structure is that for which the response is maximized in
each case.
% 
The most intense response corresponds to the \emph{up} structure centered at
0.088\,eV 
corresponding to the long-wavelength infrared radiation (LWIR) 
and reaching a $\calv^{\rmy\rmz}=87.2$ Km/s, which means the
electrons moving along $y$ (parallel to the surface) with the spin
polarized along $z$ (perpendicular to the surface),
with a speed of 87.2 Km/s.
% 
For an energy range from 0.66\,eV to 3.0\,eV, 
corresponding
to energies of the Near Infrared (NIR) to visible radiation (VIS), 
all
four systems have contributions of the same order of magnitude.
% 
For this energy range the \emph{up} structure has two peaks centered at
1.938\,eV and 1.972\,eV reaching $\calv^{\rmy\rmz}=22.2$ Km/s and
$\calv^{\rmy\rmz}=-29.7$ Km/s and the 
\emph{alt} structure has two peaks centered at 0.720\,eV
and 0.912\,eV reaching 
$\calv^{\rmy\rmz}=-40.2$ Km/s
and
$\calv^{\rmy\rmz}=-32.9$ Km/s, 
respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.906\,eV reaching 
$\calv^{\rmz\rmz}=-26.9$ Km/s, 
and the
GaAs structure response reaches the maximum centered at
2.312\,eV reaching
$\calv^{\rmx\rmx}=\calv^{\rmy\rmy}=-21.6$ Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of these values for
the 2D and bulk structures; a positive (negative) spin-velocity means that the
velocity moves (anti-)parallel to the electric field.
% 
We remark that the 2D structures have resonances that give 
larger values for $\calv^{\rma\rmb}$ than the
bulk crystals; in particular
the \emph{up} structure is
$\sim 5$ times more intense.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vsz-3d-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}

    \caption{$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)$ response
    as a function of the photon energy and polarization angle $\alpha$ for the
    \emph{up} structure for two energy ranges. The absolute maxima is located
    for an energy range from 0.08\,eV to 0.10\,eV, in the LWIR
   range, and two local maxima from 1.90\,eV to 1.93\,eV and from
    1.96\,eV to 2.0\,eV, in the VIS range, all for polarization
    angles between $25^{\circ}$ and $50^{\circ}$.}
    \label{fig:up-vsz-3d}   
\end{figure}

@@

    \caption{For the {\it up} structure and  fixing the energy to
      0.088 eV (top panel) and 1.972 eV (lower panel), 
  we show 
    $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)$ (left
    scale), the corresponding velocity angle
    $\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale), the
    collinear (green arrow) and perpendicular (blue arrow) angles.
}
    \label{fig:up-vaz-rag}
\end{figure}

@@

Using Eq. \eqref{eq:vs-mag}, we calculated 
$\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ 
and made the analysis for the case when the spin is fixed
along $z$, i.e. directed perpendicularly to the surface of the \emph{up} and
\emph{alt} structures. Also, using Eq. \eqref{eq:gamma-ang}, we determined the
angle $\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed
along the surface of the each structure.
%

\subsubsection{{\it up} structure}\label{up:fs}

We present in Fig. \ref{fig:up-vsz-3d} 
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
% (Eq. \eqref{eq:vs-mag})
for the two energy ranges of the \emph{up} structure that give the
highest values for $\calv^{\rmy\rmz}$ shown in Fig.~\ref{fig:vab-str-comp}.
% 
We obtain that the zone where the maximum response is reached corresponds to
a energy range of the incident beam from 0.084\,eV to 0.093\,eV, 
corresponding to the LWIR,
and polarization angles $\alpha$ 
between $30^{\circ}$ and $45^{\circ}$. 
Also,  two local maxima are held for same 
$\ga$ between $30^{\circ}$ and $45^{\circ}$, 
but for an energy range between 1.90\,eV and 2.05\,eV, in the VIS
range.
% %%%%%%%%%%%%%%%%% 
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%

In the top panel of Fig. \ref{fig:up-vaz-rag} we first analyze the
response for
$\hbar\go= 0.088$ eV which gives the maximum as shown
in Fig. \ref{fig:up-vsz-3d} . 
We show 
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
as a function of $\ga$
(left scale, black solid line). 
The absolute maximum is obtained when
$\alpha = 40^{\circ}$ resulting in a value of
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 95.8$\,Km/s, 
that according to Eq.~\eqref{eq:vs-mag} 
comes from 
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)=39.8$\,Km/s and
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)=87.2$\,Km/s.
% 
In the same panel we present the corresponding velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red dashed line), that for
the absolute maximum at $\ga=40^\circ$ is
$\gamma_{\mathrm{z}}(\hbar\omega=0.088\text{eV},\alpha=40^\circ) = 65^{\circ}$. 
This results means that at $\hbar\go=0.088$ eV and a polarization
angle of the incoming 
electric field of $\ga=40^\circ$ 
the electrons with a spin pointing along $z$ move at angle of 
$\gamma_{\mathrm{z}}(\hbar\omega=0.088\text{eV},\alpha=40^\circ) =
65^{\circ}$
with respect to the $x$ direction,  
with a  maximum speed
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ of  95.8 Km/s.
Also,
from Eq. \eqref{eq:gamma-par} we find that 
$\gamma^\parallel_{\mathrm{z}}(\omega,\alpha)=\ga=65.4^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 82.3$ Km/s 
(see green arrow),  
and 
that from Eq. \eqref{eq:gamma-perp}, 
$\gamma^\perp_{\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=65.5^\circ$,
gives $\ga=155.5^\circ$, with  
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 24.8$ Km/s
(see blue arrow); thus, for $\hbar\go=0.088$ eV, an
$\alpha=65.4^\circ$ ($\alpha=155.5^\circ$) gives 
electrons with spin polarized along $z$
moving 
parallel (perpendicular) to the
incident electric field,  with a speed of 82.3 (24.8) Km/s. 
% 
We also find that for all values of $\ga$,
$\gamma_{\mathrm{z}}(\omega,\alpha) =65.4^{\circ}\pm 0.3^{\circ}$,
being almost constant, and 20 Km/s $<\calv_{\gs^z}(\go,\ga)<$ 95.8 Km/s.
%

In the bottom panel of Fig. \ref{fig:up-vaz-rag}, now we take
$\hbar\go=1.972$ eV which is the local maximum 
shown in the bottom panel of Fig. \ref{fig:up-vsz-3d}. 
The local maximum is
again at  $\alpha = 40^{\circ}$ with
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) =
30.3$ Km/s and $\gamma_{\mathrm{z}}(\omega,\alpha) =
78.2^{\circ}$.
% 
In this case,  
$\alpha =\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) = 78.4^{\circ}$ with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =18.8$ Km/s 
(green circled box and arrow),
and
% 
$\gamma_{\mathrm{z}}^\perp(\omega,\alpha) = 78.5^{\circ}$, for 
$\alpha =168.5^ {\circ}$ 
(blue squared box and arrow).
% 
We find  that the velocity angle is almost constant at
$78.4^{\circ}\pm 0.3^\circ$ 
for  $0^{\circ} \leq
\alpha \leq 100^{\circ}$,
and 1 Km/s $<\calv_{\gs^z}(\go,\ga)<$ 30.3 Km/s.
% 
Although no figures are presented, we also made the analysis for the
cases when the spin polarization is directed 
along $\mathrm{x}$ and $\mathrm{y}$, finding 
the maxima for
$\hbar\go=0.088$ eV and $\alpha=40^{\circ}$, with
$\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)=37.4$ Km/s and
$\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)=24.8$ Km/s,
$\gamma_{\mathrm{x}}(\omega,\alpha) = 12.5^{\circ}$, and 
$\gamma_{\mathrm{y}}(\omega,\alpha) = 159.7^{\circ}$

@@

\subsubsection{{\it alt} structure}

We proceed to analyse the ${\it alt}$ structure, just as we did the
{\it up} structure. 
Fig. \ref{fig:alt-3d-vsb} shows
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ (Eq. \eqref{eq:vs-mag}),
where we see that
% 
the maximum response is reached for $\hbar\go=0.912$ eV
and a local maximum is obtained at
$\hbar\go=0.720$ eV, both located in the
short-wavelength infrared radiation (SWIR)
 range and for polarization angles, $\ga$,  between $120^{\circ}$ and $150^{\circ}$.

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In Fig. \ref{fig:alt-vaz-rag} we plot $\calv_{\gs^z}(\go,\ga)$ vs. $\ga$
(left scale, black solid line), fixing the energy to
0.912 eV for which the response is maximized as shown in the
top panel of Fig. \ref{fig:alt-3d-vsb}. The absolute maximum is
obtained for
$\alpha = 145^{\circ}$ with  
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 43.0$ Km/s.
% 
In the same panel we present the velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)$ vs $\ga$ (right scale, red dashed line),
that for the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) =
49.9^{\circ}$.
% 
Also, the green circle indicates
the value of $\ga$ for which the 
electrons move parallel to the incoming electric field, 
i.e. $\alpha = \gamma_{\mathrm{z}}^\parallel(\omega,\alpha) =
53.5^{\circ}$, with 
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 12.7$ Km/s. 
Likewise, the blue circle indicates
the value of $\ga$ for which the electrons move perpendicular to the
incoming electric field, i.e. 
$\alpha=140^{\circ}$, with
$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$, and 
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)=43.0$ Km/s.
% 
We also have that 
$\gamma_{\mathrm{z}}(\omega,\alpha)$ 
is centered at $51.5^{\circ}$ having
variations of $\pm 2^{\circ}$ for $0^{\circ} \leq
\alpha \leq 180^{\circ}$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
the maximum values are
$\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha) = 27.1$ Km/s and
$\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha) = 33.2$ Km/s, corresponding to 
$\gamma_{\mathrm{x}}(\omega,\alpha) = 100.1^{\circ}$
$\gamma_{\mathrm{y}}(\omega,\alpha) = 67.9^{\circ}$
and both for $\alpha=145^{\circ}$, where
the plots are not presented.

@@

 Using the Eq. \eqref{eq:vv-mag}, we calculated the
$\mathcal{V}^{\mathrm{a}} (\omega,\alpha)$ for the cases when the velocity is
fixed along the $\rma=x$ or $\rma=y$ direction on the surface of the \emph{up} and
\emph{alt} structures, and from the Eqns. \eqref{eq:polar-ang} and 
\eqref{eq:azimuthal-ang}, we determined the polar, $\theta_{\mathrm{a}}
(\omega,\alpha)$, and azimuthal, $\varphi_{\mathrm{a}} (\omega,\alpha)$, angles
corresponding to the direction of the spin.

\subsubsection{{\it up} structure}

@@

% From Sec.~\ref{up:fs}, we know that the {\it up} structure has two
% more resonant structures at $\hbar\go=1.932$ eV, and
% $\hbar\go=1.972??$ eV. For this case, where the velocity is fixed
% along $x$ or $y$, we find that

% In top and bottom panels of Fig. \ref{fig:up-3d-vva-2} we present the
% result of evaluate Eq. \eqref{eq:vv-mag} for the same structure fixing the
% velocity in the $x$ and $y$ direction for other range of energies that present
% a intense response.
% From this figure we can see that the two local maxima are obtained for energies
% between 1.80\,eV and 2.10\,eV, in the range of visible radiation, and
% polarization angles between $30^ {\circ}$ and $45^{\circ}$.
%
